\Title

### 2023-01-19 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

% !TEX encoding = UTF-8 Unicode
%!TeX TS-program = pdfLaTeX
%!TeX spellcheck = en-US
%!BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
%
% public
% https://github.com/SpikeAI/pyTERtorch/
% https://www.zotero.org/groups/4776796/fastmotiondetection

@@

>>>>

% !TEX encoding = UTF-8 Unicode
% !TeX TS-program = pdfLaTeX
% !TeX spellcheck = en-US
% !BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
%
% public
% https://github.com/SpikeAI/pyTERtorch/
% https://www.zotero.org/groups/4776796/fastmotiondetection

@@

In a review paper, we report experimental evidence for the presence of precise spiking motifs embedded in recordings from biological neural tissues~\cite{grimaldi_precise_2022}. These spatiotemporal patterns of neural activity can be an interesting representation used by neurons to perform cognitive tasks.
